\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-09-20 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
converted all the export2SESAME() names in CUBIT scripts to the new GEOCUBIT name, which is export2SPECFEM3D()
updated the manual regarding how to use "claro" and also "run_cubit2specfem3d.py"; also fixed a typo in a GEOCUBIT script

@@

@@

The mesh generated in CUBIT needs to be processed and exported in
a format compatible with SPECFEM3D. This is achieved in the Python
scripts by calling the Python-CUBIT interface functions defined in
the CUBIT directory:
\begin{enumerate}
\item Function $\mathtt{define\_bc}$ (or $\mathtt{boundary\_definition.py}$)
must be called to set up the absorbing boundaries database
\item Function $\mathtt{fault\_input}$ must be called once for each fault
to set up the fault database
\item Function $\mathtt{cubit2specfem3d.export2SESAME}$ must be called
at the very end of the script to export the mesh in a SPECFEM3D format.
\end{enumerate}
The functions in \#1 and \#3 are for the bulk and are documented in
Section \ref{subsec:Exporting-the-Mesh}. We focus here on \#2:
\begin{description}
\item [{Function:}] $\mathtt{fault\_input}$
\item [{Purpose:}] export a fault mesh database from CUBIT to a SPECFEM3D-compliant
file
\item [{Syntax:}] fault\_input(id\_fault, ids\_surf\_1, ids\_surf\_2)
\item [{Inputs:}]~\end{description}
\begin{itemize}
\item id\_fault integer index assigned to the fault. (The user must number
all the faults, starting at 1, with unit increments)
\item ids\_surf\_1 list of CUBIT ids of all surfaces that form side 1 of
the fault.
\item ids\_surf\_2 list of CUBIT ids of all surfaces that form side 2 of
the fault. (The user must decide which side of the fault is side 1.
This choice affects the sign conventions of fault quantities as explained
in Section \ref{sec:Sign-Convention-for}).\end{itemize}
\begin{description}
\item [{Outputs:}] file $\mathtt{fault\_file\_X.dat}$, where X is the
fault id (id\_fault).
\item [{Example:}] For the example in Section \ref{sec:Mesh-Generation-with}:\end{description}
\begin{lyxcode}
$\hphantom{}$A1~=~{[}168{]}

>>>>

In most cases, to re-create the meshes for the examples given, just type "claro ./block\_mesh.py" or similar 
from the command line ("claro" is the command to run CUBIT from the command line).

@@

In directory "CUBIT\_GEOCUBIT" we provide two scripts that can help doing the above tasks of exporting a CUBIT mesh
to SPECFEM3D format automatically for you: "run\_cubit2specfem3d.py" and "run\_boundary\_definition.py".
Just edit them to indicate the path to your local installation of CUBIT and also the name of the *.cub existing CUBIT mesh file
that you want to export to SPECFEM3D format. These scripts will do the conversion for you automatically except assigning material properties
to the different mesh layers. To do so, you will then need to edit the file 
called "nummaterial\_velocity\_file" that will have just been created and change it from the prototype created:

    0 1 vol1 --> syntax: \#material\_domain\_id \#material\_id \#rho \#vp \#vs \#Q\_kappa \#Q\_mu \#anisotropy
    0 2 vol2 --> syntax: \#material\_domain\_id \#material\_id \#rho \#vp \#vs \#Q\_kappa \#Q\_mu \#anisotropy

(where "vol1" and "vol2" here represent the volume labels that you have set while creating the mesh in CUBIT)
to for instance

    2 1 1500 2300 1800 9999.0 9999.0 0
    2 2 1600 2500 20000 9999.0 9999.0 0

@@

The mesh generated in CUBIT needs to be processed and exported in
a format compatible with SPECFEM3D. This is achieved in the Python
scripts by calling the Python-CUBIT interface functions defined in
the CUBIT directory:
\begin{enumerate}
\item Function $\mathtt{define\_bc}$ (or $\mathtt{boundary\_definition.py}$)
must be called to set up the absorbing boundaries database
\item Function $\mathtt{fault\_input}$ must be called once for each fault
to set up the fault database
\item Function $\mathtt{cubit2specfem3d.export2SPECFEM3D}$ must be called
at the very end of the script to export the mesh in a SPECFEM3D format.
\end{enumerate}
The functions in \#1 and \#3 are for the bulk and are documented in
Section \ref{subsec:Exporting-the-Mesh}. We focus here on \#2:
\begin{description}
\item [{Function:}] $\mathtt{fault\_input}$
\item [{Purpose:}] export a fault mesh database from CUBIT to a SPECFEM3D-compliant
file
\item [{Syntax:}] fault\_input(id\_fault, ids\_surf\_1, ids\_surf\_2)
\item [{Inputs:}]~\end{description}
\begin{itemize}
\item id\_fault integer index assigned to the fault. (The user must number
all the faults, starting at 1, with unit increments)
\item ids\_surf\_1 list of CUBIT ids of all surfaces that form side 1 of
the fault.
\item ids\_surf\_2 list of CUBIT ids of all surfaces that form side 2 of
the fault. (The user must decide which side of the fault is side 1.
This choice affects the sign conventions of fault quantities as explained
in Section \ref{sec:Sign-Convention-for}).\end{itemize}
\begin{description}
\item [{Outputs:}] file $\mathtt{fault\_file\_X.dat}$, where X is the
fault id (id\_fault).
\item [{Example:}] For the example in Section \ref{sec:Mesh-Generation-with}:\end{description}
\begin{lyxcode}
$\hphantom{}$A1~=~{[}168{]}
